A study on multicriteria ABC classification with analytical hierarchy process

### 2023-12-13 manuscript/FCPCOM/manuscript.tex
A study on multicriteria ABC classification with analytical hierarchy process

\author{Ítalo Ruan Barbosa de Aquino\fnref{label1}}
\ead{italo_ruan_@hotmail.com}

\author{Regilda da Costa e Silva Menêzes\fnref{label1}}
\ead{regilda.smenezes@ufpe.br}

@@

%%Research highlights
\begin{highlights}
\item generative method for force consistency of pairwise comparisons matrix;
\item importance of the correct balance of weights assigned to the criteria;
\item evidence of the importance of ABC multicriteria clssf for forecasting.
\end{highlights}

\begin{keyword}
multi-product batch \sep processing time maximization \sep mathematical model \sep analytical solution \sep COPSolver \sep LINGO
\end{keyword}
\end{frontmatter}

@@

\bibitem[\protect\citeauthoryear{Eilon}{1985}]{Eilon1985}
Eilon. (1985). Multi-product batch production on a single machine - A problem revisited. {\it OMEGA Int. J. of Mgmt Sci.}, Vol. 13 (5), pp. 453--468.

\bibitem[\protect\citeauthoryear{Fowler and Mönch}{2022}]{FowlerMonch2022}
Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. {\it European Journal of Operational Research}, Vol. 298, pp. 1--24.

\bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision prob-
lems - library for solving the multi-product p-batch processing time maximization problem {\it Software Impacts}, invited paper, in press.

\bibitem[\protect\citeauthoryear{Fumero \emph{et al.}}{2016}]{FumeroEtAl2016}
Fumero Y., Moreno M. S., Corsano, G., Montagna, J. M. (2016). A multiproduct batch plant design model incorporating production planning and scheduling decisions under a multiperiod scenario. {\it Applied Mathematical Modelling}, Vol. 40, pp. 3498--3515.

\bibitem[\protect\citeauthoryear{He and Hui}{2008}]{HeHui2008}
He, Y., Hui, C-W. (2008). A rule-based genetic algorithm for the scheduling of single-stage multi-product batch plants with parallel units. {\it  Computers and Chemical Engineering}, Vol. 32, pp. 3067--3083.

\bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
Kashan, A. H., and Ozturk, O. (2022). Improved MILP formulation equipped with valid inequalities for scheduling a batch processing machine with non-identical job sizes. {\it  Omega}, Vol. 112, pp. 102673.

\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.

\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
Li, C., Wang, F., Gupta, J.N.D., Chung, T. (2022). Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints. {\it Computers \& Industrial Engineering}, Vol. 169, pp. 108115.

\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.

\bibitem[\protect\citeauthoryear{Méndez \emph{et al.}}{2000}]{MendezEtAll2000}
Méndez, C.A., Henning, G.P., Cerdá, J. (2000). Optimal scheduling of batch plants satisfying multiple product
orders with different due-dates. {\it Computers and Chemical Engineering}, Vol. 24, pp. 2223--2245.

\bibitem[\protect\citeauthoryear{Méndez and Cerdá}{2003}]{MendezCerda2003}
Méndez, C.A., Cerdá, J. (2003). Dynamic scheduling in multiproduct batch plants. {\it Computers and Chemical Engineering}, Vol. 27, pp. 1247--1259.

\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.

\bibitem[\protect\citeauthoryear{Petkov and Maranas}{1998}]{PetkovMaranas1998}
Petkov, S. B., and Maranas, C. D. (1998). Design of Single-Product Campaign Batch Plants under Demand Uncertainty. {\it  AIChE Journal}, Vol. 44 (4), pp. 896--911.

\bibitem[\protect\citeauthoryear{Ravemark and Rippin}{1998}]{RavemarkAndRippin1998}
Ravemark, D. E., and Rippin, D. W. T. (1998). Optimal design of a multi-product batch plant. {\it Computers chem. Engng}, Vol. 22 (1-2), pp. 177--183.

\bibitem[\protect\citeauthoryear{Shi \emph{et al.}}{2017}]{ShiEtAll2017}
Shi, B., Qian, X., Sun, S., Yan, L. (2017). Rule-based scheduling of multi-stage multi-product batch plants with parallel units. {\it Chinese Journal of Chemical Engineering}, in press.

>>>>

\author{Beatriz Marinho Cavalcanti\fnref{label1}}
\ead{<beatriz.marinhocavalcanti@ufpe.br}

\author{Alexia Maria Duque Silva\fnref{label1}}
\ead{alexia.duque@ufpe.br}

\author{Erika Leticia Rodrigues Silva\fnref{label1}}
\ead{erika.leticias@ufpe.br}

@@

%%Research highlights
\begin{highlights}
\item generative method to force consistency of pairwise comparisons matrix;
\item importance of the correct balance of product criteria weights assigning;
\item importance of ABC multicriteria classification for forecasting.
\end{highlights}

\begin{keyword}
multicriteria classification \sep ABC classification \sep analytic hierarchy process \sep pairwise matrix consistency \sep COPSolver
\end{keyword}
\end{frontmatter}

@@

\bibitem[\protect\citeauthoryear{Flores and Whybark}{1987}]{FloresWhybark1987}
Flores, B. E., Whybark, D. C. (1987). Implementing Multiple Criteria ABC Analysis. {\it Journal of Operations Management}, Vol. 7 (1,2), pp. 79--85.

\bibitem[\protect\citeauthoryear{Fraga}{2023}]{Fraga2023}
Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multicriteria classification problem, in press.
